Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"

### 2017-11-20 paper/articleV2.tex
paper update

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad LS2N\\
$^{2}$ \quad IFSTTAR, AME, LAE\\
$^{3}$ \quad Universit\'e de Cergy-Pontoise}

@@

The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements. To the best of our knowledge, no efficient coding scheme has been proposed for large-scale sensor network. We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}). The proposed method computes and encodes third-octave bands $L_{eq}$ with controllable precision, enabling low bitrate transmissions while allowing both the derivation of other acoustic indicators and the implementation of offline audio event detection schemes. We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates. Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

@@

In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a widely used reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}. This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter on 2~s third-octave bands measurements. We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

Thus, the impact of the frame rate parameter of the proposed encoding scheme on intelligibility is evaluated. To do so, a perceptual test is conducted. For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used. The dataset is composed of 9 french sentences enunciated by 3 male and 3 female speakers. The sentences have an mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8. The 54 extracts are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total. However, as the recording conditions are the same for all extracts the speaker identity is considered as a source of variability rather than as a necessary factor in the test statistics. As a result the objective is primarily to evaluate the 9 sentences with 4 encoding frame rates, \textit{i.e.} 36 parameters.

Several subjective intelligibility metrics are standardized in the literature such as the system proposed in \cite{itup835}. However, metrics regarding the signal only (SIG) or background noise only (BAK) which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with an uncontrollable SNR by the encoding process. Given these conditions a subjective score on the whole signal is used similarly to the OVRL score. As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words. For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject. For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible). The first metric is directly the score attributed by the listener, referred as the intelligibility score (IS). The second metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.

@@

This test requires an implementation of the inverse operation of the coding process to provide the listener with an estimate of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. In fact, each white square can be interpreted as the filter applied to obtain a single third-octave band. The filtering process will average the energy content of the signal over the corresponding band. As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis. This leads to the phenomenon seen on Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions. The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not. The time-domain signal is then retrieved using the overlap-add method. When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.

@@

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad LS2N\\
$^{2}$ \quad IFSTTAR, AME, LAE\\
$^{3}$ \quad ETIS, UMR 8051, Universit\'e Paris Seine, Universit\'e Cergy-Pontoise, ENSEA, CNRS, F-95000 Cergy-Pontoise.}

@@

The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements. We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}). The proposed method computes and encodes third-octave bands $L_{eq}$ with controllable precision, enabling low bitrate transmissions while allowing both the derivation of other acoustic indicators and the implementation of offline audio event detection schemes. We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates. Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

@@

In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}. This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements. We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration. Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts. The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions. As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands. For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.

@@

Thus, the impact of the frame rate parameter of the proposed encoding scheme on intelligibility is evaluated. To do so, a perceptual test is conducted. For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used. The dataset is composed of 9 french sentences enunciated by 3 male and 3 female speakers. The sentences have a mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8. The 54 extracts are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total. However, as the recording conditions are the same for all extracts the speaker identity is considered as a source of variability rather than as a necessary factor in the test statistics. As a result the objective is primarily to evaluate the 9 sentences with 4 encoding frame rates, \textit{i.e.} 36 parameters.

Several subjective intelligibility metrics are standardized in the literature such as the system proposed in \cite{itup835}. However, metrics regarding the signal only (SIG) or background noise only (BAK) which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with an uncontrollable SNR by the encoding process. Given these conditions a subjective score on the whole signal is used similarly to the OVRL score in \cite{itup835}. As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words. For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject. For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible). The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper. The second metric is directly the score attributed by the listener, referred as the intelligibility score (IS).

@@

This test requires an implementation of the inverse operation of the coding process to provide the listener with an estimate of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Each white square can be interpreted as the filter applied to obtain a single third-octave band. The filtering process will average the energy content of the signal over the corresponding band. As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis. This leads to the phenomenon seen on Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions. The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not. The time-domain signal is then retrieved using the overlap-add method. When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.

@@

This scheme will be implemented with a large-scale sensor grid as part of the CENSE project, where sensors are designed to be low-cost and energy efficient. The aim of the project is to create noise maps by linking standard acoustic measurements with novel perceptually motivated metrics. The presented coding scheme will enable a thorough study of the correlation between sound sources and context with pleasantness as perceived by the citizens to better understand the composition of acoustic scenes in urban environments.

### 2017-11-20 paper/sensors/coverLetter.tex
paper update

$\rightarrow$ This is now more clearly dscussed in the introduction as well as in the conclusion where a dedicated paragraph has been added.

CATHERINE: Est-il possible de dédier un petit paragraphe à la question dans la conclusion?

>>>>

$\rightarrow$ This is now more clearly discussed in the introduction as well as in the conclusion where a dedicated paragraph has been added on the use of this scheme as part of the current project.
